\mytitile\\~

### 2020-01-30 document.tex
Merge branch 'dm'
# Conflicts:
#	document.tex

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic}. Their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics, and high controllability of their parameters 
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the decoherence rates 
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, main experiments in on-chip quantum 
optics with intense propagating light were 
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of such composite structures with intense free 
radiation. While there were studies on dressing 
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with free 
radiation is no less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar waveguide while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only calls forth multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs and free radiation have 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint\cite{chow2010detecting} readout of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown 
depicting the layout of the components. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in colour on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

As one can see, various multiphoton transitions besides 
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$ 
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in feature I. A 
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, it is involved in forming features II and 
III. Notably, transitions $11/2$, ${21/3}$ and 
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Red dashed line shows the 
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R$. \textbf{(d)} Transitions in the 
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed red line. Next, 
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $\omega_1$, single-photon driving by 
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon driving by $\hat H_d^2$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know 
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace. Unfortunately, all matrix elements of $\hat V = \hat V_J$ are zero in both our degenerate subspaces, so technically any choice of zero-order states will diagonalize it. In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V \ket{n}$. 
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.

@@

For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$)
\renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{equation}
	M_{15} =\kbordermatrix{&\ket{a,0} & \ket{a, 2}\\
	\ket{a,0}&\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
	\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\
	\ket{a, 2}&\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
	\frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}}.
\end{equation}
The normalized eigenvectors 
\begin{equation}
\ket{N} = C_n \ket{n} + C_{n'}\ket{n'}, 
\ket{N'} = C'_{n}\ket{n} + C'_{n'}\ket{n'}
\end{equation}
of the matrix are the desired zero-order superpositions. Next, we first-order correct them as usual:
\begin{equation}
	\ket{N}+\ket{N^{1}} = \sum_{j=n,n'} C_{j}\ket{j} + \sum_{j\ne n, n'}\ket{j}\frac{\bra{j}\hat V\ket{N}}{E_n-E_j}.
\end{equation}

>>>>

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic,Qopt_1300refs}. Their Hamiltonians can be pre-designed
and engineered which makes them a particularly 
versatile tool for studies in quantum optics, and high controllability of their parameters
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the relaxation and decoherence rates
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, experiments with intense driving fields resulting in the dressing effects in on-chip quantum optics  were
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes (A-T) splittings of
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of similar composite structures with intense driving field. While there were studies on dressing
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with external dressing field is not less attractive since its
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar antenna while its state can be
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only results in multiphoton transitions of
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs under strong driving field
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} (maximal Josephson energies $E^1_{J,
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
charging energies $E^{1,2}_C/h = 220$ MHz, asymmetries $d^{1,2} =0.75$) coupled
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint readout \cite{chow2010detecting} of
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown, where the layout of the components is presented. The
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in color on the sides; their SQUIDs are
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

@@

As one can see, various multiphoton transitions besides
the main lines at $\omega_{(1,2)}(I)/2\pi$ (or 
$01$ and $10$ lines) are visible. The ${02/2}$ and ${20/2}$
are very commonly found for transmons and lie 
$|\alpha_{(1,2)}|/2$ lower than the main lines 
$\omega_{(1,2)}(I)$. Another two-photon process 
appears as $11/2$ line when two SAAs are excited 
simultaneously. This process is used, for 
example, for doing the bSWAP 
gate\cite{poletto2012entanglement}; in our case, 
it is taking part in feature I. A
three-photon process $12/3$ is also clearly 
visible just below the $02/2$ line. As we will 
see, processes $12/3$~and~$21/3$ are involved in forming features III and II, respectively. Notably, transitions $11/2$, ${21/3}$ and
${12/3}$ are forbidden when there is no 
interaction between transmons ($J=0$). Therefore, 
it is expected that all Roman-numbered features 
should only appear with non-vanishing $\hat 
H_{int}$.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{main_scheme_2}  
	\caption{Explaining feature III. \textbf{(a)} 
	Schematic of the transition frequencies near 
	III (not to scale). Black dashed line shows the
	current (0.36 mA) where the first transmon 
	(orange) is below the second one (blue) 
	exactly by $\alpha_2/2$ and several 
	transitions become resonant. Here we assume 
	that each transmon is driven at its own 
	frequency. \textbf{(b)} System level 
	structure at the resonant point and the first transmon 
	driving of amplitude $\Omega_1$ 
	(orange ellipses) at a small detuning 
	$\Delta_1$ from $\omega_1$. The second 
	transmon driving is not shown here. Action of 
	$\hat H_{int}$ in RWA is depicted as 
	orange-blue circles. \textbf{(c)} In the 
	frame rotating with $\hat 
	H_{d}^1$, states $\ket{0j},\ket{1j}$ 
	become nearly degenerate ($\omega_1 
	\rightarrow \Delta_1$). Dressing increases this splitting to 
	$\Omega_1^R$. \textbf{(d)} Transitions in the
	dressed system induced by $\hat 
	H_{d}^2$ (coupled level subspaces are shown with blue ellipses). In 
	the left part of the panel, all possible 
	two-photon transitions near $\omega_1$ are 
	depicted: the blue transitions are not 
	shifted in frequency, the light blue ones are shifted 
	by $\pm\Omega^R_1/2$. In the right 
	part, the most contributing trajectories are 
	depicted; gray crosses show transitions that 
	are forbidden without the coupling $J$.}
	\label{fig:main_scheme}
\end{figure}

@@

In \autoref{fig:main_scheme}, we elaborate on which transitions
are involved in the A-T-like effect for feature III. 
For simplicity, we will temporarily assume that 
each transmon is driven at its own frequency 
(this assumption will be lifted in the following 
section). For convenience, in 
\autoref{fig:main_scheme}~(a) we schematically 
reproduce the transitions near III where the 
first transmon (orange) is below the second 
(blue), and the resonance point in current is 
shown with a dashed black line. Next,
\autoref{fig:main_scheme}~(b) demonstrates the 
level structure of the SAM at 0.36 mA. Detuned by 
$\Delta_1$ from $\omega_1$, single-photon driving by
$\hat H_d^1$ is shown with orange ellipses while 
much weaker two-photon driving by $\hat H_d^2$ is not shown because it does not alter the structure of energy levels. Since from numerical simulations we know
that the third level of the first transmon is not 
necessary to observe the splitting, $\ket{20}$ is 
shown transparent, and states $\ket{21},\ 
\ket{22}$ are not shown.

@@

The choice of zero-order state vectors $\ket{N^0}$ from a degenerate subspace is arbitrary because any linear combination of basis vectors $\ket{n}$ from this subspace will satisfy the unperturbed Schrödinger equation. However, if we demand the \textit{change} of $\ket{N^0}$ to be small under the perturbation $\hat V$, they become determined and are given by diagonalization of $\hat V$ in the degenerate subspace. Unfortunately, all matrix elements of $\hat V = \hat V_J$ are zero in both our degenerate subspaces, so technically any choice of zero-order states will diagonalize it. In other words, the degeneracy is not lifted in the first-order, and thus we have to diagonalize the matrix\cite{landau2013quantum}
\begin{equation}
	M_{nn'} = \sum\limits_{m}\frac{V_{ nm}V_{mn^\prime}}{E_n-E_m}.
\end{equation}
Here, $\ket{n}$ and $\ket{n'}$ are the basis 
states from the degenerate subspace with energy 
$E_n$, and $V_{mn} = \bra{m} \hat  V_J \ket{n}$.
The sum is over all other zero-order states 
$\ket{m}$ outside the degenerate subspace.

@@

For example, in our case for one of the degenerate subspaces ($E_n^0 = -\Omega_1/2,\ \hat V = \hat V_J$) we obtain the following matrix:
\renewcommand{\kbldelim}{[}% Left delimiter
\renewcommand{\kbrdelim}{]}% Right delimiter
\begin{equation}
	M_{15} =\kbordermatrix{&\ket{a,0} & \ket{a, 2}\\
	\ket{a,0}&\frac{J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
	\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)}\\
	\ket{a, 2}&\frac{\sqrt{2} J^{2} \Omega_{1}}{\alpha \left(2 \Omega_{1} - \alpha\right)} &
	\frac{2 J^{2} \left(\Omega_{1} - \alpha\right)}{\alpha \left(2 \Omega_{1} - \alpha\right)}}.
\end{equation}
The normalized eigenvectors 
\begin{equation}
\ket{N} = C_n \ket{n} + C_{n'}\ket{n'}, 
\ket{N'} = C'_{n}\ket{n} + C'_{n'}\ket{n'}
\end{equation}
of the matrix are the desired zero-order superpositions. Next, we first-order correct them as usual:
\begin{equation}
	\ket{N}+\ket{N^{1}} = \sum_{j=n,n'} C_{j}\ket{j} + \sum_{j\ne n, n'}\ket{j}\frac{\bra{j}\hat V\ket{N}}{E_n-E_j}.
\end{equation}
